Short and Mechanized Logical Relation for Dependent Type Theory

### 2024-02-20 paper/paper.tex
Minor

We present our definitions and proofs in set theory notation and
terminology rather than in Coq syntax to make the material accessible
to readers with general mathematical background. However, we make the
typeset definitions as close as possible to our mechanization so the
definitions and the proofs can be easily encoded in a proof
assistant.
We find the close correspondence
between our typeset presentation and the Coq development advantageous
for a couple of reasons.

>>>>

We present our definitions and proofs in set theory notation and
terminology rather than in Coq syntax to make the material accessible
to readers with general mathematical background. However, notation
aside, the typeset representation is purposefully made to be closer to
our mechanization so less massaging of the definitions is required to
encode our proofs in a proof assistant.  The close correspondence
between a typeset proof and a mechanized proof comes at the potential
risk that the artifacts specific to theorem provers are reflected upon
the presented proof. However, for proofs by logical relation for
dependent types, we find our approach advantageous for a few
reasons.
First, unlike properties that are derivable through
syntactic means, proof by logical relation is demanding on the
strength of the metatheory. An informal proof that attempts to be
agnostic or merely ambiguous about the underlying metatheory

However, we make the
typeset definitions as close as possible to our mechanization so the
definitions and the proofs can be easily encoded in a proof
assistant.
We find the close correspondence
between our typeset presentation and the Coq development advantageous
for a couple of reasons. First, compared to other proof techniques,
such as the use of preservation and progress to derive syntactic
soundness, defining a logical relation for a dependently typed
language is demanding on the strength of the metatheory.
